\abstract{
This dissertation presents the search for flavor changing neutral currents in processes with top pairs where one top decays through the flavor changing neutral current decay mode (to an up type quark and a photon) and the other decays through the most common standard model mode to a b-quark and a W boson.  The W boson then decays leptonically defining the channels searched (electron+jets and muon+jets).  Using the entire Run-2 data set of $\sqrt{s} = 13$ TeV data collected using the ATLAS experiment between 2015 and 2018 corresponding to a total integrated luminosity of 139  fb$^{-1}$.  Observation of the flavor changing neutral current decays in top quarks would be an unambiguous sign of physics beyond the standard model.  
A neural network was developed to separate signal and background events using both low level kinematic variables as well as physics guided high level variable combinations as inputs.  The candidate signal events contain an isolated very high $p_T$ photon, a lepton (either an electron or muon), a b-tagged jet, at least one more light jet, and missing transverse energy.  Various data driven techniques were used to estimate contributions to the background from events with a hard scatter photon or a photon faked by either a jet or an electron.  As there is no sensitivity for observation upper limits on the observed (expected) branching ratio and cross section of this flavor changing neutral current process are set: BR($t\rightarrow q \gamma$)$<$ $9.6\times10^{-5}$ $(11.0^{+4 .3}_{-3.0}\times10^{-5})$ and $\sigma$($pp\rightarrow t\bar{t} \rightarrow bWq\gamma$) $< 50 (60)$fb.

%Need to end with this statement if you're working from papers published or soon to be published.
This dissertation includes previously unpublished co-authored material.
}