\author{Jason Tyler Barkeloo}
\school{University of Oregon, Eugene, Oregon}%Graduate school
\school{Miami University, Oxford, Ohio}
\school{Wittenberg University, Springfield, Ohio}%Undergraduate school

\degree{Doctor of Philosophy, Physics, 2020, University of Oregon}%Change year
\degree{Master of Sceience, Physics, 2012, Miami University}
\degree{Bachelor of Science, Physics, 2010, Wittenberg Univeristy}%Undergraduate degree

%%There is a known issue if you do not fill in the interests section.  If you want to skip this section, comment out line#526 of uothesis.cls file \cvitem{GRANTS, AWARDS AND HONORS}{\@awards}
%\interests{}%Your interests. French movies, long walks on the beach, baking tarts...

\position{\textbf{University of Oregon}, Graduate Research Assistant, ATLAS Experiment, June 2014-Present}
\position{\textbf{University of Oregon}, Graduate Teaching Assistant, September 2012-June 2014}%Your job while at UO, probably graduate research assistant.
\position{\textbf{Miami University}, Teaching and Research Assistant, August 2010 - May 2012}
\position{\textbf{Wittenberg University}, Undergraduate Researcher, August 2008 - May 2010}


\award{Weiser Senior Teaching Assistant Award -- University of Oregon --  2014}%If you didn't get any awards you'll have to comment out things in the uothesis. I dug up something from my undergraduate
\award{American Association of Physics Teachers Outstanding Teaching Assistant -- Miami University -- 2012}

\publication{A. Hachtel, J. Kleykamp, D. Kane, M. Marshall, B. Worth, J. Barkeloo, J. Kangara, J. Camenisch, M. Gillette, S. Bali. “An undergraduate lab on measurement of radiative broadening in atomic vapor”,  Am. J. Phys. \textbf{81}(6), 471 (2013).}
\publication{J. Kangara, A. Hachtel, M. C. Gillette, J. Barkeloo, E. Clements, S. Bali. “Design and construction of cost-effective fail-safe tapered amplifier systems for laser cooling and trapping experiments”, Am. J. Phys. \textbf{82}(8), 805 - 817 (2014).}
%Fill this out with your publications.

