\newpage
\section{Introduction}
\label{sec:intro}
%Deep thoughts go here.

The Standard Model of particle physics has proven itself an exceptional and resilient theory since the combination of the electromagnetic and weak interactions in 1961\cite{SM1Glashow}.  Further theoretical work combined the Higgs Mechanism\cite{Higgs1,Higgs2} with the electroweak theory\cite{SM2Weinberg, SM3Salam}.  The resiliency of this theoretical model has been tested to further degrees of accuracy over the decades with one of my most recent portions being the experimental confirmation of the Higgs Boson in 2012\cite{Higgs3,Higgs4} using the Large Hadron Collider (LHC).  Further precision measurements are ongoing at various experiments at the LHC, including the ATLAS experiment.

However, the Standard Model is known to have flaws and disagreements with nature.  For example, the Standard Model predicts massless neutrinos which is in conflict with experimental observation of neutrino flavor oscillation and doesn't provide an explanation for dark matter particles or their interactions with currently known particles.  While these large gaps in the Standard Model are well known every precision measurement made has yet to give any significant new hints toward physics beyond the Standard Model.  One new pathway to look for these hints at the LHC is through top quark decays.

\subsection{The Standard Model Top Quark}
The top quark was first observed at Fermilab's Tevatron in 1995\cite{TopObs} but the increase in energy and amount of data at the LHC has produced orders of magnitude more top quarks than previously seen opening up a pathway to precision measurements of the properties of the top quark.  The top quark is the heaviest fundamental particle with a mass of 172.51 $\pm$ 0.27 (stat) $\pm$ 0.42 (syst)\cite{TopMass2017}.  This large mass also means that top top quark lifetime is very short (5 * 10$^{-25}$ s) and decays before it can hadronize.  This allows us to probe its' branching ratios and decay modes directly.  The Standard Model predicts that the top quark decays through the charged current mode nearly 100\% of the time; t$\rightarrow$ qW (q = b,s,d)\cite{PDG2018}.   The Standard Model also predicts a rare branching ratio of the top quark through a flavor changing neutral current (FCNC) process, to a neutral boson (photon, Z boson, Higgs Boson, or gluon) and up type quark with a branching ratio on the order of 10$^{-14}$.

\subsection{Searching for FCNC Top Quark Decays}
Precision measurements are an important litmus test for the Standard Model.  Predicted branching ratios for FCNC processes in top quark decays are far beyond the experimental reach of the LHC and any observation of these decay modes would be a sure sign of new physics.  Branching ratios are an important measurement due to a litany of theories for new physics beyond the Standard Model (BSM).  These BSM theories predict enhancements in the top sector by many orders of magnitude such as Minimal Supersymmetric models\cite{MSSM}, R-parity-violating Supersymmetic models\cite{RPVSUSY} and two Higgs doublet models\cite{2HDM} can all increase this branching ratio many orders of magnitude.  Even a null result to a search will set an upper limit on the branching ratio that can assist in ruling out future physical models based on their amount of large top sector enrichment.

This dissertation presents a search for top FCNCs using the entire Run 2 dataset at the LHC, containing combined 2015-2018 datasets taken by the ATLAS experiment totaling 139 fb$^{-1}$ of integrated luminosity taken at $\sqrt{s}$= 13 TeV.  The analysis presented looks for an excess of events coming from top quark pair produced events where one top quark decays to the most likely decay mode (a bottom quark and W boson) and the other to an up type quark (up or charm) and a photon. Section \ref{ch:Theory} a theoretical background will be presented for both the Standard Model with a closer view on the usual extensions to include the FCNC vertices.  Following this  Section \ref{ch:LHCDetector} will discuss the LHC and the ATLAS experiment used in the creation of the dataset used in the analysis.  In Section \ref{ch:Simulation} the special signal simulation requirements will be presented as well as the common background event simulation methodology.  The search strategy including the creation of signal, control and validation regions and the training of a neural network will be examined in Section \ref{ch:SearchStrategy}.  Section \ref{ch:Results} will discuss the results and the conclusions drawn from these results will be presented in Chapter \ref{ch:Conclusion}.